CLT Results

### 2022-03-30 analysis/clt_irt_analysis.Rmd
add bayes freq comparison

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)

@@

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.9)
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

firt_1F <- mirt(firt_dat, 1, itemtype = "3PL")
firt_2F <- mirt(firt_dat, 2, itemtype = "3PL")

@@

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)

anova(firt3,firt2)

summary(firt_2F)
```
```{r}
coefs2PL <- coef(firt2,
     simplify = T,
     IRTpars = T)$items%>%
  as_tibble(rownames = "item")
```

@@

# plot chart
ggplot(format, aes(Theta, P.1, col = aoa_german_comb, group = item)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  #facet_wrap(~targetWord)+
  ylim(0,1)+
  scale_color_viridis_c(name = "AoA") +
  #geom_hline(aes(yintercept = 0.5)) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```
```{r}
plot(firt2, type='trace', which.item = c(1:43), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
              theta_lim = c(-6, 6), 
     main = "")
```

```{r}
for(i in 1:length(firt_dat)){
  ItemPlot <- itemfit(firt2, 
                      group.bins=15,
                      empirical.plot = i,
                      empirical.CI = .95,
                      method = 'ML') 
  print(ItemPlot)
}
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)

@@

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.9),
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",technical = list(NCYCLES = 1000))

@@

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000), SE = T)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)

anova(firt1,firt2)

summary(firt_2F)
```

```{r}
coefs2PL <- coef(firt2,
     as.data.frame = TRUE,
     IRTpars = T)%>%
  as_tibble(rownames = "x")%>%
  separate(x, into = c("item", "nlpar"), sep = "\\.", remove = T)%>%
  mutate(nlpar = recode(nlpar,
                       b = "Easiness",
                       a = "Discrimination"
                      ))%>%
  filter(nlpar != "g", nlpar != "u", item != "GroupPars")
```

@@

# plot chart
ggplot(format, aes(Theta, P.1, col = aoa_german_comb, group = item)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  #facet_wrap(~targetWord)+
  ylim(0,1)+
  scale_color_viridis_c(name = "AoA") +
  #geom_hline(aes(yintercept = 0.5)) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```

# Compare Bayesian and Frequentist models

```{r}
pc <- bind_rows(
format%>%
  select(-item, -P.0)%>%
  rename(item = targetWord,
         p = P.1,
         theta = Theta)%>%
  mutate(source = "frequentist"),
icc3%>%
  mutate(source = "bayesian")
)

pc %>% 
  ggplot(aes(x = theta, y = p, group = source, col = source)) +
  geom_line() +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  facet_wrap(~item)+
  #guides(col = F)+
  scale_color_colorblind() +
  labs(x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()

```
```{r}
params%>%left_join(coefs2PL)%>%
  mutate(slope = ifelse(nlpar == "Easiness", -1,1))%>%
  ggplot(aes(x = Estimate, y = par))+
  geom_abline(aes(slope = slope, intercept = 0), lty = 3, alpha = .5)+
  geom_errorbar(aes(ymin = CI_2.5, ymax = CI_97.5), alpha = .25, col = "dodgerblue")+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), alpha = .25, col = "dodgerblue")+
  geom_point(pch = 1, alpha = .75)+
  facet_grid(~nlpar)+
  labs(x = "Bayesian estimate", y = "Frequentist estimate")+
  stat_cor()+
  #ylim(-10,10)+
  #xlim(-10,10)+
  #coord_fixed(ratio = 1)+
  scale_color_viridis_c()+
  theme_bw()
```
